\LARGE \bf Expectation-Maximization based defense mechanism for distributed Model Predictive Control

### 2022-02-22 article/article.tex
correct arrows in figures

          \draw[latex-,thick] (block1.east)+(0,.3) -- ( {$(block1.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{1}[k]$};
          \draw[-latex,thick] (block1.east)+(0,-.3) -- ( {$(block1.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta}_{1}[k]$};

          \draw[latex-,thick] (blockM.east)+(0,.3) -- ( {$(blockM.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{M}[k]$};
          \draw[-latex,thick] (blockM.east)+(0,-.3) -- ( {$(blockM.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta_{M}}[k]$};

@@

          \draw[latex-,thick] (block1.east)+(0,.3) -- ( {$(block1.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{1}[k]$};
          \draw[-latex,thick] (block1.east)+(0,-.3) -- ( {$(block1.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta}_{1}[k]$};

@@

          \draw[latex-,thick] (blockM.east)+(0,.3) -- ( {$(blockM.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{M}[k]$};
          \draw[-latex,thick] (blockM.east)+(0,-.3) -- ( {$(blockM.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta_{M}}[k]$};

>>>>

          \draw[-latex,thick] (block1.east)+(0,.3) -- ( {$(block1.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{1}[k]$};
          \draw[latex-,thick] (block1.east)+(0,-.3) -- ( {$(block1.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta}_{1}[k]$};

          \draw[-latex,thick] (blockM.east)+(0,.3) -- ( {$(blockM.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{M}[k]$};
          \draw[latex-,thick] (blockM.east)+(0,-.3) -- ( {$(blockM.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta_{M}}[k]$};

@@

          \draw[-latex,thick] (block1.east)+(0,.3) -- ( {$(block1.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{1}[k]$};
          \draw[latex-,thick] (block1.east)+(0,-.3) -- ( {$(block1.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta}_{1}[k]$};

@@

          \draw[-latex,thick] (blockM.east)+(0,.3) -- ( {$(blockM.east)+(0,.3)$} -| coordinator.west) node [above,midway] {$\tilde{\vec{\lambda}}_{M}[k]$};
          \draw[latex-,thick] (blockM.east)+(0,-.3) -- ( {$(blockM.east)+(0,-.3)$} -| coordinator.west) node [below,midway] {$\vec{\theta_{M}}[k]$};
